Parametric analysis of ambisonic audio

### 2020-07-05 Chapters/Conclusions.tex
beta_v3

>>>>

\newpage
\section{List of Contributions}

In the following list we show the main scientific contributions, as main author, related to this dissertation:

\begin{itemize}

	\item Peer-reviewed journal articles

	\textbf{"Analysis of spherical isotropic noise fields with an A-Format tetrahedral microphone"}.
	\underline{A. P\'erez-L\'opez} and N. Stefanakis.
	\textit{The Journal of the Acoustical Society of America 146.4 (2019): EL329-EL334.}

	\item Peer-reviewed conference articles

	\textbf{"Blind reverberation time estimation from ambisonic recordings"}.
	\underline{A. P\'erez-L\'opez}, A. Politis and E. G\'omez.
	Submitted to \textit{IEEE 22nd International Workshop on Multimedia Signal Processing, 2020.}\\

	\textbf{"PAPAFIL: a low complexity sound event localization and detection method with parametric particle filtering and gradient boosting".}
	\underline{A. P\'erez-L\'opez} and R. Ibañez-Usach.
	Submitted to \textit{Detection and Classification of Acoustic Scenes and Events 2020 Workshop (DCASE2020)}.\\

	\textbf{"A hybrid parametric-deep learning approach for sound event localization and detection".}
	\underline{A. P\'erez-L\'opez}, E. Fonseca and X. Serra.
	In \textit{Proceedings of the Detection and Classification of Acoustic Scenes and Events 2019 Workshop (DCASE2019)}.

	\textbf{"Ambiscaper: A tool for automatic generation and annotation of reverberant ambisonics sound scenes".}\\
	\underline{A. P\'erez-L\'opez}.
	In \textit{Proceedings of the 16th International Workshop on Acoustic Signal Enhancement (IWAENC). IEEE, 2018.}

	\item Conference engineering briefs

	\textbf{"Ambisonics directional room impulse response as a new convention of the spatially oriented format for acoustics".}
	\underline{A. P\'erez-L\'opez} and J. De Muynke.
	In \textit{Proceedings of the 144th Audio Engineering Society Convention. Audio Engineering Society, 2018.}\\

	\textbf{"pysofaconventions, a Python API for SOFA".}
	\underline{A. P\'erez-L\'opez}.
	In \textit{Proceedings of the 148th Audio Engineering Society Convention. Audio Engineering Society, 2020.}\\

	\textbf{"A Python library for multichannel acoustic signal processing".}
	\underline{A. P\'erez-L\'opez} and A. Politis.
	In \textit{Proceedings of the 148th Audio Engineering Society Convention. Audio Engineering Society, 2020.}\\

\end{itemize}

Moreover, although not strictly aligned with the research direction of this thesis, the author has supervised the following publication:\\

	 \textbf{"Sound event localization and detection based on CRNN using dense rectangular filters and channel rotation data augmentation".}
	F. Ronchini, D. Arteaga and \underline{A. P\'erez-L\'opez}.
	Submitted to \textit{Detection and Classification of Acoustic Scenes and Events 2020 Workshop (DCASE2020)}.\\

\newpage
\section{List of Software Resources}

As a result of the development of this thesis, the following open-source libraries and repositories have been produced. All of them are freely available through the author's GitHub page \cite{andresgithub} under open-source licenses.

\begin{itemize}

	\item Software tools:

	\href{https://github.com/andresperezlopez/masp}{masp: Multichannel Acoustic Signal Processing library} 
		Tools for acoustic simulation and spherical array processing. \\

	\href{https://github.com/andresperezlopez/pysofaconventions}{pysofaconventions} Implementation of the SOFA convention in Python.\\

	\href{https://github.com/andresperezlopez/AmbisonicsDRIR}{AmbisonicsDRIR}	 Ambisonic SOFA Convention proposal.\\

	\href{https://github.com/andresperezlopez/ambiscaper}{AmbiScaper} Tool for automatic generation of annotated ambisonic datasets.\\

	\item Method implementations:

	\href{https://github.com/andresperezlopez/ambisonic_rt_estimation}{ambisonic\_rt\_estimation} Contains the code implementing the methods described in Chapter~\ref{chap:rt60}.\\

	\href{https://github.com/andresperezlopez/DCASE2020}{DCASE2020} Full code implementing the SELD algorithm from Chapter~\ref{chap:seld2019}.\\

	\href{https://github.com/andresperezlopez/DCASE2019_task3}{DCASE2019\_task3} 
		Implementation of the method submitted to DCASE2019 (not included in this thesis). \\

\end{itemize}

### 2020-07-05 manuscript.tex
beta_v3

%%%%%% Thanks
\noindent {\Large \sffamily Thanks} thanks to....  \todo{thanks}

@@

%PREFACE. 
{\bf Preface \todo{TODO}}

@@

>>>>

%%%%%% Thanks
\noindent {\Large \sffamily Thanks}\\

First of all, I must thank my supervisors, Emilia and Adan, who have made possible the realization of this journey.

Thanks to all my friends from the Audio Team at Eurecat: Umut, Julien, Tim, Niklas, Toni, Gerard, Andrés, John, Stefan, Marc. And also to  the people from Image and the Visualization teams. I spent last four years working with the finest of the companies.

Thanks also to all the great people I met at the MTG, including Pritish, Xavier, and specially Edu for the logistic and intellectual help. I would like to give public acknowledgment to Xavier Serra for his successful task of leading and gathering such unique international group of talented people.

Special thanks to Nikos and all the Signal Processing Lab crew for warmly welcoming me in Heraklion, and helping me in many different ways in your lovely place. I hope to come back there soon.

Many thanks to Archontis and Tuomas for the visit opportunity, and for all the  facilities they gave me in my stay in this amazing place called Tampere. I take the opportunity to say hello and thanks to Kostas, Natalya, Annamaria, Toni, and all the nice people there.

Thanks to Max, who has been always very receptive and supportive on numerous occasions, and has indirectly contributed to the success of this project. 
Thanks also to Rafa, who decided to get on board for some unknown reason.

Thanks to all the friends I made and preserved in Barcelona in the last four years. Special thanks to my musician family from Balkumbia, Fanfarrai and Telewawachi Kilili; I learned a lot from you. Special acknowledgements for the good times with the people in Can Collet (best farm-school in town) and the Valencian oldies.

Thanks a lot to Chedar for his company in these final steps. And, of course, million thanks to my family and to Marta for their unconditional love and support.\\

To all of you: thanks.

@@

%PREFACE. 
%{\bf Preface }
\section*{\Large \sffamily  Preface}

The present thesis has been carried out within the context of the Industrial Doctorate program from the Catalan government, as a collaboration between the Music Technology Group of the Pompeu Fabra University, and the Multimedia Unit of Eurecat, the Catalan Technology Center. 
It has been jointly supervised by Dr. Emilia Gómez and Dr. Adan Garriga.

The industrial nature of the doctorate program implies a tendency towards the innovative application of the findings and conclusions generated during the development of the thesis. 
Therefore, one of the targets of the research performed in the context of this thesis is the stress on real-world problems, scenarios and technologies, with the aim of developing methods that could be easily adapted into applications with a high level of technology readiness. 
Moreover, there has been also an stress on research reproducibility. This has not been motivated only by an academic perspective; but also by the open research and open innovation paradigms present in our today's society.\\

The work presented here would not have been possible without the contributions from an excellent network of researchers. Apart from internal collaborations (UPF and Eurecat), two of the main contributions in the thesis followed two research visits to internationally recognized institutions: the Audio Research Group from Tampere University, Finland (Chapter~\ref{chap:rt60}), and the Signal Processing Group at the FORTH - Foundation for Research and Technology Hellas, Heraklion, Greece, (Chapter~\ref{chap:coherence}).

The alphabetical list of academic collaborators is: Eduardo Fonseca, Emilia G\'omez, Rafael Ib\'añez-Usach,  Julien de Muynke, Archontis Politis, Xavier Serra, and Nikolaos Stefanakis.

@@

%\begin{appendices}
%\appendixpage
%\noappendicestocpagenum
%\addappheadtotoc

%\chapter{List of Contributions}
%
%In the following list we show the main scientific contributions, as main author, related to this dissertation:
%
%\begin{itemize}
%
%	\item Peer-reviewed journal articles
%	
%	\textbf{"Analysis of spherical isotropic noise fields with an A-Format tetrahedral microphone"}.
%	\underline{A. P\'erez-L\'opez} and N. Stefanakis.
%	\textit{The Journal of the Acoustical Society of America 146.4 (2019): EL329-EL334.}
%
%	\item Peer-reviewed conference articles
%
%	\textbf{"Blind reverberation time estimation from ambisonic recordings"}.
%	\underline{A. P\'erez-L\'opez}, A. Politis and E. G\'omez.
%	Submitted to \textit{IEEE 22nd International Workshop on Multimedia Signal Processing, 2020.}\\
%
%	\textbf{"PAPAFIL: a low complexity sound event localization and detection method with parametric particle filtering and gradient boosting".}
%	\underline{A. P\'erez-L\'opez} and R. Ibañez-Usach.
%	Submitted to \textit{Detection and Classification of Acoustic Scenes and Events 2020 Workshop (DCASE2020)}.\\
%	
%	\textbf{"A hybrid parametric-deep learning approach for sound event localization and detection".}
%	\underline{A. P\'erez-L\'opez}, E. Fonseca and X. Serra.
%	In \textit{Proceedings of the Detection and Classification of Acoustic Scenes and Events 2019 Workshop (DCASE2019)}.
%	
%	\textbf{"Ambiscaper: A tool for automatic generation and annotation of reverberant ambisonics sound scenes".}\\
%	\underline{A. P\'erez-L\'opez}.
%	In \textit{Proceedings of the 16th International Workshop on Acoustic Signal Enhancement (IWAENC). IEEE, 2018.}
%	
%	
%	\item Conference engineering briefs
%
%
%	\textbf{"Ambisonics directional room impulse response as a new convention of the spatially oriented format for acoustics".}
%	\underline{A. P\'erez-L\'opez} and J. De Muynke.
%	In \textit{Proceedings of the 144th Audio Engineering Society Convention. Audio Engineering Society, 2018.}\\
%	
%	\textbf{"pysofaconventions, a Python API for SOFA".}
%	\underline{A. P\'erez-L\'opez}.
%	In \textit{Proceedings of the 148th Audio Engineering Society Convention. Audio Engineering Society, 2020.}\\
%	
%	\textbf{"A Python library for multichannel acoustic signal processing".}
%	\underline{A. P\'erez-L\'opez} and A. Politis.
%	In \textit{Proceedings of the 148th Audio Engineering Society Convention. Audio Engineering Society, 2020.}\\
%	
%\end{itemize}
%
%\newpage
%
%Moreover, although not strictly aligned with the research direction of this thesis, the author has supervised the following publication:\\
%
%	 \textbf{"Sound event localization and detection based on CRNN using dense rectangular filters and channel rotation data augmentation".}
%	F. Ronchini, D. Arteaga and \underline{A. P\'erez-L\'opez}.
%	Submitted to \textit{Detection and Classification of Acoustic Scenes and Events 2020 Workshop (DCASE2020)}.\\
%
%
%
%\chapter{List of Software Resources}
%
%
%As a result of the development of this thesis, the following open-source libraries and repositories have been produced. All of them are freely available through the author's GitHub page \cite{andresgithub} under open-source licenses. 
%
%
%\begin{itemize}
%
%	\item Software tools:
%
%	\begin{itemize}
%	
%		\item \href{https://github.com/andresperezlopez/masp}{masp: Multichannel Acoustic Signal Processing library} 
%		Tools for acoustic simulation and spherical array processing. 
%		 
%		
%		\item \href{https://github.com/andresperezlopez/pysofaconventions}{pysofaconventions} Implementation of the SOFA convention in Python. 
%	
%		\item \href{https://github.com/andresperezlopez/AmbisonicsDRIR}{AmbisonicsDRIR}	 Ambisonic SOFA Convention proposal.
%
%		\item \href{https://github.com/andresperezlopez/ambiscaper}{AmbiScaper} Tool for automatic generation of annotated ambisonic datasets.
%
%	\end{itemize}
%	\newpage
%	\item Method implementations: 
%
%	\begin{itemize}
%		\item \href{https://github.com/andresperezlopez/ambisonic_rt_estimation}{ambisonic\_rt\_estimation} Contains the code implementing the methods described in Chapter~\ref{chap:rt60}.
%	
%		\item \href{https://github.com/andresperezlopez/DCASE2020}{DCASE2020} Full code implementing the SELD algorithm from Chapter~\ref{chap:seld2019}.
%	
%		\item \href{https://github.com/andresperezlopez/DCASE2019_task3}{DCASE2019\_task3} 
%		Implementation of the method submitted to DCASE2019 (not included in this thesis). 
%
%	\end{itemize}
%
%\end{itemize}
%

%\end{appendices}
